Research log

### 2024-01-10 docs/ExploratoryResults.Rmd
exploratory results
updated path to Hangman data

load('E2.click_log_with_boards.RData')

@@

load('E4.click_log.RData')

load('E4.click_log_with_boards.RData')

load('E4.judge_df.RData')

>>>>

load('../experiments/Battleships2/data/batch1/click_log_with_boards.RData')

@@

load('../experiments/Hangman2/data/E4.click_log.RData')

load('../experiments/Hangman2/data/E4.click_log_with_boards.RData')

load('../experiments/Hangman2/data/E4.judge_df.RData')
